---
title: "Data Visualisation Project Part 1"
author: "Lavanya N"
date: "4/18/2021"
output: html_document
---

```{r, echo=FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
source('https://raw.githubusercontent.com/iascchen/VisHealth/master/R/calendarHeat.R')
```

# 1. Visualising AirBnB Occupancies and Revenue Generated Over Time

Calendar heatmaps are often used to discern patterns, trends, and anomalies over time in a calendar-like interface. In this case, they can be used to understand how AirBnB occupancies and revenue generated over change over the period of 2019 to 2020.

```{r, echo=FALSE}
first2019 <- read.csv('Calendar Data/first2019.csv')
second2019 <- read.csv('Calendar Data/second2019.csv')
combined2019 <- rbind(first2019, second2019)
combined2019 <- combined2019 %>% mutate(booked = ifelse(available == 'f', 1, 0))
combined2019$price <- as.integer(str_replace(combined2019$price, '.', ''))

occupancy_2019 <- combined2019 %>% group_by(date = date) %>% 
  summarise(totalBooked = sum(booked, na.rm = TRUE), totalListings = n()) %>% 
  mutate(percent_booked = (totalBooked/totalListings)*100)

revenue_2019 <- combined2019 %>% filter(booked == 1) %>% group_by(date = date) %>%
  summarise(totalRevenue = sum(price, na.rm = TRUE), 
            avgRevenue = mean(price, na.rm = TRUE))
```

```{r, echo=FALSE}
first2020 <- read.csv('Calendar Data/first2020.csv')
second2020 <- read.csv('Calendar Data/second2020.csv')
combined2020 <- rbind(first2020, second2020)
combined2020 <- combined2020 %>% mutate(booked = ifelse(available == 'f', 1, 0))
combined2020$price <- as.integer(str_replace(combined2020$price, '.', ''))

occupancy_2020 <- combined2020 %>% group_by(date = date) %>% 
  summarise(totalBooked = sum(booked, na.rm = TRUE), totalListings = n()) %>% 
  mutate(percent_booked = (totalBooked/totalListings)*100)

revenue_2020 <- combined2020 %>% filter(booked == 1) %>% group_by(date = date) %>%
  summarise(totalRevenue = sum(price, na.rm = TRUE), 
            avgRevenue = mean(price, na.rm = TRUE))
```

# a. Total Occupancies in 2019 and 2020

We can see that total occupancies in 2019 were generally at least twice that of occupancies in 2020.

```{r, echo=FALSE}
combined_occupancy <- rbind(occupancy_2019, occupancy_2020)
```

```{r,echo=FALSE}
calendarHeat(combined_occupancy$date, combined_occupancy$totalBooked, 
             ncolors = 99, color = 'g2r', varname = 'Total Occupancies in New York City')
```

# b. Occupancy Rates in 2019 and 2020

Occupancy rates are severely reduced in 2020.

```{r, echo=FALSE}
calendarHeat(combined_occupancy$date, combined_occupancy$percent_booked, 
             ncolors = 99, color = 'g2r', varname = 'Occupancy Rates in New York City')
```

# c. Total Daily Revenue in 2019 and 2020

Total daily revenue decreased from about 6 million dollars a day to 2 or 3 million dollars a day.

```{r, echo=FALSE}
combined_revenue <- rbind(revenue_2019, revenue_2020)
```

```{r, echo=FALSE}
calendarHeat(combined_revenue$date, combined_revenue$totalRevenue, 
             ncolors = 99, color = 'r2b', varname = 'Total Daily Revenue in New York City')
```

# d. Average Daily Revenue in 2019 and 2020

Average daily revenues are also lower in 2020.

```{r, echo=FALSE}
calendarHeat(combined_revenue$date, combined_revenue$avgRevenue, 
             ncolors = 99, color = 'r2b', varname = 'Average Daily Revenues in New York City')
```

# 2. Seasonal Changes in AirBnB Occupancy and Revenue Generated

We can view the same patterns using line graphs instead.

```{r, echo=FALSE}
ggplot(data = combined_occupancy, aes(x = as.Date(date), y = totalBooked)) +
  geom_point(color = '#007A87', alpha = 0.5) +
  geom_smooth(color = '#FF5A5F') +
  scale_x_date(date_labels = '%b %y') +
  labs(title = 'Total Occupancies in New York City') +
  ylab('Total Bookings') +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none',
        axis.title.x = element_blank())
```

```{r, echo=FALSE}
ggplot(data = combined_occupancy, aes(x = as.Date(date), y = percent_booked)) +
  geom_point(color = '#007A87', alpha = 0.5) +
  geom_smooth(color = '#FF5A5F') +
  scale_x_date(date_labels = '%b %y') +
  labs(title = 'Occupancy Rates in New York City') +
  ylab('Occupancy Rate (%)') +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none',
        axis.title.x = element_blank())
```

```{r, echo=FALSE}
ggplot(data = combined_revenue, aes(x = as.Date(date), y = totalRevenue)) +
  geom_point(color = '#007A87', alpha = 0.5) +
  geom_smooth(color = '#FF5A5F') +
  scale_x_date(date_labels = '%b %y') +
  labs(title = 'Total Daily Revenue in New York City') +
  ylab('Total Revenue ($)') +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none',
        axis.title.x = element_blank())
```

```{r, echo=FALSE}
ggplot(data = combined_occupancy, aes(x = as.Date(date), y = totalBooked)) +
  geom_point(color = '#007A87', alpha = 0.5) +
  geom_smooth(color = '#FF5A5F') +
  scale_x_date(date_labels = '%b %y') +
  labs(title = 'Average Daily Revenue in New York City') +
  ylab('Average Revenue ($)') +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none',
        axis.title.x = element_blank())
```

# 3. Data Tables on Occupancy and Revenue of AirBnBs in New York City

The data tables allow users to see the number of bookings, listings, percentage of listings booked, total revenue, and average revenue for any day that they select.

```{r, echo=FALSE}
library(DT)
```

```{r, echo=FALSE}
datatable(combined_occupancy, filter = 'top', options = list(searchHighlight = TRUE)) %>%
  formatRound(~percent_booked, digits = 0)
```

```{r, echo=FALSE}
datatable(combined_revenue, filter = 'top', options = list(searchHighlight = TRUE)) %>%
  formatRound(~totalRevenue + avgRevenue, digits = 0)
```

# 4. Understanding Trends in AirBnB Reviews

The patterns in the reviews are similar to those in the occupancy and revenue trends.

```{r, echo=FALSE}
reviews <- read.csv('Reviews Data/reviews.csv')
reviews_summary <- reviews %>% group_by(date) %>% summarise(totalReviews = n())
reviews_summary$percent_reviews <- reviews_summary$totalReviews/combined_occupancy$totalBooked
```

```{r, echo=FALSE}
ggplot(data = reviews_summary, aes(x = as.Date(date), y = totalReviews)) +
  geom_point(color = '#007A87', alpha = 0.5) +
  geom_smooth(color = '#FF5A5F') +
  scale_x_date(date_labels = '%b %y') +
  labs(title = 'Total Daily Reviews in New York City') +
  ylab('Total Reviews') +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none',
        axis.title.x = element_blank())
```

On average, we see that only 1.5% of guests leave reviews.

```{r, echo=FALSE}
ggplot(data = reviews_summary, aes(x = as.Date(date), y = percent_reviews)) +
  geom_point(color = '#007A87', alpha = 0.5) +
  geom_smooth(color = '#FF5A5F') +
  scale_x_date(date_labels = '%b %y') +
  labs(title = 'Percentage of Bookings Reviewed in New York City') +
  ylab('Review Percentage (%)') +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none',
        axis.title.x = element_blank())
```

# 5. What Makes a Host a Superhost?

We were interested to know what makes a host a superhost. We believe that response and acceptance rates could be linked closely to it.

```{r, echo=FALSE}
listings <- read.csv('Listings Data/jan2021_listings.csv')
superhost <- listings %>% select(host_response_time, host_response_rate, host_acceptance_rate, host_has_profile_pic, host_identity_verified, host_is_superhost)
superhost[superhost == 'N/A'] <- NA
superhost <- na.omit(superhost)
superhost$host_acceptance_rate <- as.integer(str_replace(superhost$host_acceptance_rate, '%', ''))
superhost$host_response_rate <- as.integer(str_replace(superhost$host_response_rate, '%', ''))
superhost_summary <- superhost %>% group_by(host_is_superhost) %>% summarise(avgResponse = mean(host_response_rate, na.rm = TRUE), avgAcceptance = mean(host_acceptance_rate, na.rm = TRUE), hostPic = sum(host_has_profile_pic == 't'), hostIdentity = sum(host_identity_verified == 't'))
superhost_summary <- superhost_summary[2:3, ]
```

```{r}
ggplot(data = superhost_summary, aes(x = host_is_superhost, y = avgResponse, fill = host_is_superhost)) +
  geom_col(width = 0.5) +
  labs(title = 'Average Response Rates of Superhosts and Non-Superhosts') +
  ylab('Response Rates (%)') +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none',
        axis.title.x = element_blank())
```

```{r, echo=FALSE}
ggplot(data = superhost_summary, aes(x = host_is_superhost, y = avgAcceptance, fill = host_is_superhost)) +
  geom_col(width = 0.5) +
  labs(title = 'Average Acceptance Rates of Superhosts and Non-Superhosts') +
  ylab('Acceptance Rates (%)') +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none',
        axis.title.x = element_blank())
```
